Complete Real-Time Liver Model Including Glisson's Capsule, Vascularization and Parenchyma

### 2013-05-30 Doc/Vrst2013/vrst2013.tex
vrst2013: more changes
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@577 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

% NOT required for Proceedings
%\keywords{deformable liver model, Glisson's capsule, vascularization, real-time soft tissue modeling}
\keywords{deformable liver model}

@@

Moreover, if we neglect the time-dependent behaviour we are able to reproduce
the measurements presented in~\cite{Hollenstein2006} with less than 1\% error.
Simulating the pressure of 3\,MPa and setting the elastic parameters to
$E_p$=30\,kPa for parenchyma and $E_c$=3\,MPa and $t$=93\,$\mu$m for capsule.
All the values lie within the measurements specified in the paper.
\TG{add figure?}

@@

\section{Future Work} %{{{

\TG{including vascularization; global deformation; stress the complexity of validation of global deformations}

@@

\section{Conclusions} %{{{
\TG{TODO}
In the paper, a complete model of the liver was presented taking into account 
three constituents of the organ, each being modelled with a different type 
of finite elements: tetrahedral corotational model used for the parenchyma, serially 
linked corotational beams based on Tymoshenko formulation employed to model the vascularization 
and finally CST elements used for the capsule. 
The model was first validated for local displacements: the aspiration test presented in~\cite{Hollenstein2006} 
was successfully reproduced, showing a good agreement between the simulation and experiments. 
Further, the model was used to demonstrate global influence of the capsule when the organ 
undergoes large deformations.

In the future work, we plan to employ the proposed model for other organs where the capsule play an important role
(for example kidneys). We will also focus on better description of the mechanical interactions and couplings among the organs and tissues in the abdominal 
cavity via realistic modeling of boundary conditions using mechanical constraints and contacts.

>>>>

% NOT required for Proceedings
%\keywords{deformable liver model, Glisson's capsule, real-time soft tissue modeling}
\keywords{deformable liver model}

@@

Moreover, if we neglect the time-dependent behaviour we are able to reproduce
the measurements presented in~\cite{Hollenstein2006,Nava2008} with less than 1\% error.
In this case the simulation is performed with the pressure of 30\,kPa and with
the following elastic parameters: $E_p$=30\,kPa for parenchyma and $E_c$=3\,MPa
and $t$=93\,$\mu$m for capsule. All the values lie within the measurements
specified in the paper. \TG{add figure?}

@@

\section{Present and Future Work} %{{{

Presently we are working on the validation of the model also in context of
global deformations where we believe the capsule plays also an essential role.
This task is however complicated by the lack of biomechanical literature
dealing with the response of the capsule.
%The influence of the capsule on local level has been published in literature
%before. However, to our knowledge it's influence on global scale deformation
%has not been studied yet. We believe that the capsule has non-negligible impact
%also on global level.

Our goal is to create complete liver model suitable for real-time medical
simulations. For this a model accounting for all three main constituents
(parenchyma, vascularization and capsule) is necessary. To achieve that we have
integrated our model with the with the vasularization method proposed
in~\cite{Peterlik2012}. In our future work we need to validate the model in the
context of global and local deformations. This task is challenging because
comparing in vivo measurements with the simulation is difficult due to complex
boundary conditions. 
\TG{ex-vivo: no information abou vessels; phantoms: cannot model capsule}

@@

\section{Conclusions} %{{{

In the paper we presented a liver model accounting for the Glisson's capsule, a component that is often overlooked. Each constituent being modelled with a different type 
of finite elements: tetrahedral corotational model used for the parenchyma and
and CST membrane elements used for the capsule. 
The model was validated for local displacements based on the the aspiration test presented in~\cite{Hollenstein2006} 
was successfully reproduced, showing a good agreement between the simulation and experiments.

%Further, the model was used to demonstrate global influence of the capsule when the organ 
%undergoes large deformations.

%In the future work, we plan to employ the proposed model for other organs where the capsule play an important role
%(for example kidneys). We will also focus on better description of the mechanical interactions and couplings among the organs and tissues in the abdominal 
%cavity via realistic modeling of boundary conditions using mechanical constraints and contacts.
